Using HbA1c and Fasting BG to Predict Development of CFRD

### 2025-03-24 Christine Chan/CF Registry/cf_registry_CFRD_prediction.qmd
notes from meeting with Kristen

```{r setup}
#| include: false
library(survival)
library(nlme)
library(JM)
library(dplyr)
library(tidyr)
knitr::opts_knit$set(root.dir = "/home/timvigers/OneDrive/Vigers/CF/Christine Chan/CF Registry")
```

@@

>>>>

```{r setup}
#| include: false
library(survival)
library(nlme)
library(JM)
library(dplyr)
library(tidyr)
home_dir <- switch(Sys.info()["sysname"],
  "Darwin" = "/Users/timvigers/Library/CloudStorage/OneDrive-TheUniversityofColoradoDenver/Vigers/CF/Christine Chan/CF Registry",
  "Linux" = "/home/timvigers/OneDrive/Vigers/CF/Christine Chan/CF Registry"
)
knitr::opts_knit$set(root.dir = home_dir)
```

@@

- Check for HbA1c measures after the survival time (not sure if needs to be strictly less than)
- Set parameterization = "slope" to see if change in HbA1c increases hazard 
- Look into dynamic predictions in JMBayes
- Could try re-fitting this with a left-censored model 
  - If it says the same thing, it's probably okay to use the right-censored
  - Could also try using the half interval model Kristen described
